Housing Market Institutions Drive Race and Ethnicity Differences in Energy Consumption

### 2015-04-01 ConferencePaper/DraftEdwardsWoods.tex
Did some splitting of text into paragraphs and created a table for the system results.

This project sets out to derive an explanation for the effect on housing selection by household characteristics.  The choice of housing, differentiates between renters and owners: owners and those households making payments towards ownership are treated as the same.  Homes are categorized by structure type.   
Housing choice is of importance for several reasons.  First, housing choices may be linked to fundamental characteristics of the heads of households as a dependent variable that has implications as to utility, and in this respect it is assumed that owning a detached home is of greatest use.  The choice of homes is considered cardinal, where a house is of greatest value and the mobile home is treated as the least appealing choice.  A townhome, row house, in a desirable location such as an urban area, may be a highly desirable good, in general that is not treated as the norm. Structures other than detached houses may be considerably more perishable.  This assumption is made regardless of variations within the desirability of particular detached houses. Second, the choice of purchasing or renting a home is relevant within the structure types.  An individual may choose to forego ownership of a townhouse in favor of renting a house, or forego owning a mobile home in favor of renting an apartment.  Here, both from a utilitarian perspective of the need for one domicile over another is considered as well as prestige that comes from both the structure type as well as what utility may derive from ownership.

@@

Lastly, the effect of home ownership and structure choice may have implications for future outcomes of the children of the suggested households.  In that respect, it can be said that there is evidence of children having better outcomes, in terms of education and income, than their peers in households that choose to rent (Boehm 2014).  It is plausible that the outcome benefits are coming from a causal relationship with parental characteristics rather than that of the housing choice, and are co-variables, rather than having an internal causal relationship.  While it is beyond the scope of this paper, it is also plausible that housing choice is indicative of neighborhood choice, though it should be stated that there is no assertion on this statement to be found here.
It is also of note that households choice of structure type, payment method, and location are often very difficult to change based on the history of a household (Darrah 2014).  That is, that households that have tended towards renting, have difficulty or at least choice not, to buy in the future.  Rather, community attitudes and behaviors in relation to housing are often sticky in changing, and this is of importance as related to the outcomes of children; often mirroring the characteristics of their parents.  
Until this point the role of race has not been mentioned in the development of the motivation for this paper.  It should be stated here that it is assumed that race has no direct impact on the housing choices made.  Rather, race may help to stand as a proxy for cultural differences in behaviors that are persistent.  While there is no sufficient explanation for why race appears to make a difference in housing choices, to does appear that it plays a role.
To sum, this paper explores the relationship between the household characteristics and the choice of housing structure, and suggests that there is reason in particular of choosing housing structures based on wealth and needs as a proxy for utility, which not only has immediate effects but those that have persistent effects on the legacy of households.  While the utility of a particular domicile cannot be measured directly, it is assumed that the choice of structure is indicative of the value that the household places on one choice over another.

0
\begin{itemize}

  \item Differences in energy use by race and ethnicity is frequently reported in the literature
  \item Much of the difference has to do with differences in income levels and education but not frequently modeled correctly.
  \item Even with proper race and ethnicity controls with income, some patterns persist.
  \item We assert that these differences are caused, at least in part, by housing discrimination, forcing people into housing types different than what they would prefer without discrimination; and renting rather than buying.
  \item We show this with a model that endogenizes structure type and tenure decision.
  \item emphasize that this is early work.
\end{itemize}

@@

The RASS data set includes 25721 observations from households.  Of these observations, many respondents to the survey left questions blank and thus those respondent’s information is omitted from the analysis.  Nonetheless, 20,303 observations are included in applying the model.   Observations are taken from households across the state of California and the initial phase of the RASS consisted of a mail out survey that in total had a 20% response rate (RASS Methodology 21) across stratums.  While the data set includes 564 variables only a small portion of those are used to construct our model.
  First, our dependent variable is constructed by combing dwelling type (dwltype) and the binary response variable Ownrent.  Dwltype includes six categories as follows: single family detached house, townhouse (including duplex, or row house), small apartment complex, large apartment complex, mobile home, and other.  For our purposes the category of other was dropped from the analysis.  As well mobile homes are noted with having considerably fewer observations than other categories.  Thus, we end with ten categories, the previous five dwelling types combined with whether the household is renting/leasing or buying/own the home.
	Next, our independent variables are as follows: income, resident ages, education, and ethnicity.  Income is categorized into twelve separate options ranging from less than ten thousand to over one hundred and fifty thousand dollars total annually. Resident characteristics describe the number of individuals in the household including children, adults, and seniors.  Education is broken into six categories describing highest education level completed by the head of the household: elementary, some high school, high school. Some college/trade/vocational school, college graduate and post graduate degree.  The ethnicity variable is constructed from a composite of six dummy variables for head of households broken into head of households one and two.  The result is one variable for each where from one to six: Native American, Asian/Pacific Islander, Black/African American, Hispanic/Latino, White/Caucasian, and Other.  For our purposes head of household #2 is ignored.

@@

% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:08:48 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Mobile & SFDetached & SFAttached & SmApartment & LgApartment \\ 
  \hline
FALSEWt & 371 & 5694 & 544 & 430 & 951 \\ 
  FALSEAfAm &  24 & 754 & 121 & 174 & 382 \\ 
  FALSEAsian &   1 & 231 &  48 &  52 & 113 \\ 
  FALSEMulti &   6 &  87 &  14 &  12 &  27 \\ 
  FALSENativeAm &   7 &  35 &   9 &   7 &  15 \\ 
  FALSEOther &   2 &  59 &   8 &  13 &  29 \\ 
  FALSEPacific &   1 &  22 &   1 &   2 &  10 \\ 
  TRUEAfAm &   3 &   8 &  10 &   5 &   8 \\ 
  TRUEAsian &   0 &   5 &   0 &   0 &   1 \\ 
  TRUEMulti &   1 &  10 &   2 &   4 &   4 \\ 
  TRUENativeAm &   2 &  17 &   3 &   6 &   9 \\ 
  TRUEOther &   6 &  41 &  12 &  16 &  24 \\ 
  TRUEPacific &   0 &   2 &   1 &   1 &   0 \\ 
  TRUEWt &  97 & 730 & 105 & 184 & 332 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Race and Structure Type} 
\label{tab:RaceVStruct}
\end{table}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:08:48 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Mobile & SFDetached & SFAttached & SmApartment & LgApartment \\ 
  \hline
NE &  47 & 1173 & 218 & 326 & 470 \\ 
  MidWest &  92 & 2080 & 162 & 145 & 323 \\ 
  South & 245 & 2685 & 257 & 226 & 603 \\ 
  West & 137 & 1757 & 241 & 209 & 509 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Region and Structure Type} 
\label{tab:RegionVStruct}
\end{table}
\begin{figure}
\begin{center}
\caption{Annual kWh by Rent/Own and Race}
\label{fig:kWhbyOwnRace}
\includegraphics{DraftEdwardsWoods-005}
\end{center}
\end{figure}

@@

% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:08:54 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & FALSE & TRUE \\ 
  \hline
FALSEWt & 7606 & 384 \\ 
  FALSEAfAm & 1367 &  88 \\ 
  FALSEAsian & 424 &  21 \\ 
  FALSEMulti & 133 &  13 \\ 
  FALSENativeAm &  68 &   5 \\ 
  FALSEOther & 102 &   9 \\ 
  FALSEPacific &  30 &   6 \\ 
  TRUEAfAm &  31 &   3 \\ 
  TRUEAsian &   4 &   2 \\ 
  TRUEMulti &  19 &   2 \\ 
  TRUENativeAm &  36 &   1 \\ 
  TRUEOther &  88 &  11 \\ 
  TRUEPacific &   4 &   0 \\ 
  TRUEWt & 1330 & 118 \\ 
   \hline
\end{tabular}
\caption{EnergyStar Wall AC by Race and Ethnicity} 
\label{tab:EnergyStarWall}
\end{table}

% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:08:54 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & Rural & Urban \\ 
  \hline
FALSEWt & 1937 & 6053 \\ 
  FALSEAfAm & 192 & 1263 \\ 
  FALSEAsian &  14 & 431 \\ 
  FALSEMulti &  28 & 118 \\ 
  FALSENativeAm &  25 &  48 \\ 
  FALSEOther &  12 &  99 \\ 
  FALSEPacific &   4 &  32 \\ 
  TRUEAfAm &   6 &  28 \\ 
  TRUEAsian &   0 &   6 \\ 
  TRUEMulti &   1 &  20 \\ 
  TRUENativeAm &   3 &  34 \\ 
  TRUEOther &   5 &  94 \\ 
  TRUEPacific &   2 &   2 \\ 
  TRUEWt & 137 & 1311 \\ 
   \hline
\end{tabular}
\caption{Race by Urban/Rural} 
\label{tab:UrbRural}
\end{table}

% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:08:54 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & NG & LPG & Oil & Kerosene & Elec & Wood & Solar & Other \\ 
  \hline
FALSEWt & 4077 & 315 & 361 &   3 & 3190 &  11 &  12 &   7 \\ 
  FALSEAfAm & 755 &  17 &  35 &   0 & 640 &   0 &   2 &   0 \\ 
  FALSEAsian & 312 &   7 &  12 &   0 & 109 &   0 &   0 &   2 \\ 
  FALSEMulti &  85 &   5 &   3 &   0 &  53 &   0 &   0 &   0 \\ 
  FALSENativeAm &  34 &   2 &   1 &   0 &  36 &   0 &   0 &   0 \\ 
  FALSEOther &  57 &   3 &   6 &   0 &  44 &   0 &   0 &   0 \\ 
  FALSEPacific &  15 &   0 &   2 &   0 &  17 &   0 &   2 &   0 \\ 
  TRUEAfAm &  20 &   0 &   1 &   0 &  13 &   0 &   0 &   0 \\ 
  TRUEAsian &   5 &   0 &   0 &   0 &   1 &   0 &   0 &   0 \\ 
  TRUEMulti &  12 &   0 &   1 &   0 &   8 &   0 &   0 &   0 \\ 
  TRUENativeAm &  29 &   0 &   0 &   0 &   8 &   0 &   0 &   0 \\ 
  TRUEOther &  62 &   1 &   5 &   0 &  30 &   0 &   0 &   0 \\ 
  TRUEPacific &   1 &   1 &   0 &   0 &   2 &   0 &   0 &   0 \\ 
  TRUEWt & 830 &  33 &  26 &   0 & 552 &   0 &   1 &   0 \\ 
   \hline
\end{tabular}
\caption{Water Service by Race and Ethnicity} 
\label{tab:Water}
\end{table}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:08:54 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrrr}
  \hline
 & NG & LPG & Oil & Kerosene & Elec & Wood & Solar & District & Other \\ 
  \hline
FALSEWt & 3987 & 400 & 642 &  40 & 2515 & 245 &   1 &  11 &  19 \\ 
  FALSEAfAm & 674 &  29 &  60 &   6 & 640 &  10 &   0 &   5 &   0 \\ 
  FALSEAsian & 249 &   1 &  21 &   0 & 122 &   1 &   0 &   2 &   0 \\ 
  FALSEMulti &  80 &   6 &   7 &   0 &  41 &   7 &   0 &   0 &   1 \\ 
  FALSENativeAm &  34 &   3 &   1 &   0 &  33 &   2 &   0 &   0 &   0 \\ 
  FALSEOther &  59 &   1 &   9 &   0 &  36 &   3 &   0 &   0 &   0 \\ 
  FALSEPacific &  16 &   0 &   2 &   0 &   5 &   1 &   0 &   0 &   0 \\ 
  TRUEAfAm &  21 &   0 &   1 &   1 &   9 &   0 &   0 &   0 &   0 \\ 
  TRUEAsian &   4 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 \\ 
  TRUEMulti &  11 &   0 &   4 &   0 &   4 &   1 &   0 &   0 &   0 \\ 
  TRUENativeAm &  26 &   1 &   2 &   0 &   7 &   0 &   0 &   0 &   0 \\ 
  TRUEOther &  53 &   0 &   8 &   1 &  32 &   0 &   0 &   2 &   0 \\ 
  TRUEPacific &   1 &   0 &   0 &   0 &   2 &   0 &   0 &   0 &   0 \\ 
  TRUEWt & 604 &  25 &  51 &   2 & 540 &  18 &   0 &   3 &   1 \\ 
   \hline
\end{tabular}
\caption{Heating Fuel by Race and Ethnicity} 
\label{tab:HeatFuel}
\end{table}
% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:08:54 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & VColdCold & HotDryMixedDry & HotHumid & MixedHumid & Marine \\ 
  \hline
FALSEWt & 3118 & 850 & 1216 & 2382 & 424 \\ 
  FALSEAfAm & 299 & 131 & 383 & 611 &  31 \\ 
  FALSEAsian &  95 & 128 &  60 &  77 &  85 \\ 
  FALSEMulti &  51 &  27 &  13 &  40 &  15 \\ 
  FALSENativeAm &  23 &  10 &   7 &  28 &   5 \\ 
  FALSEOther &  29 &  16 &  24 &  37 &   5 \\ 
  FALSEPacific &   4 &   6 &  13 &   4 &   9 \\ 
  TRUEAfAm &  16 &   5 &   4 &   9 &   0 \\ 
  TRUEAsian &   2 &   2 &   1 &   0 &   1 \\ 
  TRUEMulti &  12 &   6 &   1 &   0 &   2 \\ 
  TRUENativeAm &   9 &  14 &   1 &   8 &   5 \\ 
  TRUEOther &  35 &  19 &  10 &  28 &   7 \\ 
  TRUEPacific &   2 &   0 &   2 &   0 &   0 \\ 
  TRUEWt & 237 & 481 & 406 & 237 &  87 \\ 
   \hline
\end{tabular}
\caption{Climate by Race and Ethnicity} 
\label{tab:Climate}
\end{table}
\begin{figure}
\begin{center}
\caption{Age of Structure by Rent/Own and Race/Ethnicity}
\label{fig:AgebyOwnRace}
\includegraphics{DraftEdwardsWoods-013}
\end{center}
\end{figure}

@@

% latex table generated in R 3.1.3 by xtable 1.7-4 package
% Fri Mar 27 15:08:56 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & Never & ThreeDay & TwoDay & OneDay & FewWeek & OneWeek & LessWeek \\ 
  \hline
FALSEWt &  67 & 452 & 1814 & 3303 & 1825 & 254 & 275 \\ 
  FALSEAfAm &  11 & 156 & 351 & 341 & 448 &  80 &  68 \\ 
  FALSEAsian &   4 &  63 & 111 & 148 &  91 &  13 &  15 \\ 
  FALSEMulti &   2 &  14 &  45 &  40 &  36 &   7 &   2 \\ 
  FALSENativeAm &   0 &   7 &  22 &  27 &  11 &   3 &   3 \\ 
  FALSEOther &   2 &  10 &  25 &  21 &  43 &   3 &   7 \\ 
  FALSEPacific &   0 &   3 &   9 &  10 &  11 &   0 &   3 \\ 
  TRUEAfAm &   1 &   4 &   7 &  13 &   9 &   0 &   0 \\ 
  TRUEAsian &   0 &   0 &   1 &   3 &   2 &   0 &   0 \\ 
  TRUEMulti &   0 &   2 &   1 &  11 &   5 &   2 &   0 \\ 
  TRUENativeAm &   0 &   3 &  12 &  15 &   4 &   2 &   1 \\ 
  TRUEOther &   0 &  20 &  28 &  31 &  14 &   3 &   3 \\ 
  TRUEPacific &   0 &   3 &   0 &   1 &   0 &   0 &   0 \\ 
  TRUEWt &  22 & 208 & 453 & 435 & 226 &  42 &  62 \\ 
   \hline
\end{tabular}
\caption{Weekly Meals Cooked by Race and Ethnicity} 
\label{tab:Cooking}
\end{table}
\begin{figure}
\begin{center}
\caption{Daytime Temp and Race/Ethnicity (Winter)}
\label{fig:TempHomeRace}
\includegraphics{DraftEdwardsWoods-015}
\end{center}
\end{figure}

@@

***NEED TEXT TO EXPLAIN HERE***

>>>>

The choice of housing, differentiated between renters and owners: owners and those households making payments towards ownership are treated as the same.  Homes are categorized by structure type.

Housing choices may be linked to fundamental characteristics of the heads of households as a dependent variable that has implications as to utility, and in this respect it is assumed that owning a detached home is of greatest use.  The choice of homes is considered cardinal, where a house is of greatest value and the mobile home is treated as the least appealing choice.  A townhome, row house, in a desirable location such as an urban area, may be a highly desirable good, in general that is not treated as the norm. Structures other than detached houses may be considerably more perishable.  This assumption is made regardless of variations within the desirability of particular detached houses. The choice of purchasing or renting a home is relevant within the structure types.  An individual may choose to forego ownership of a townhouse in favor of renting a house, or forego owning a mobile home in favor of renting an apartment.  Here, both from a utilitarian perspective of the need for one domicile over another is considered as well as prestige that comes from both the structure type as well as what utility may derive from ownership.

@@

The effect of home ownership and structure choice may have implications for future outcomes of the children of the suggested households.  In that respect, it can be said that there is evidence of children having better outcomes, in terms of education and income, than their peers in households that choose to rent (Boehm 2014).  It is plausible that the outcome benefits are coming from a causal relationship with parental characteristics rather than that of the housing choice, and are co-variables, rather than having an internal causal relationship.  While it is beyond the scope of this paper, it is also plausible that housing choice is indicative of neighborhood choice, though it should be stated that there is no assertion on this statement to be found here.

Households choice of structure type, payment method, and location are often very difficult to change based on the history of a household (Darrah 2014).  Households that have tended towards renting have difficulty, or at least choose not to, buy in the future.  Community attitudes and behaviors in relation to housing are often sticky in changing, and this is of importance as related to the outcomes of children; often mirroring the characteristics of their parents.

This paper explores the relationship between the household characteristics and the choice of housing structure, and suggests that there is reason in particular of choosing housing structures based on wealth and needs as a proxy for utility, which not only has immediate effects but those that have persistent effects on the legacy of households.  While the utility of a particular domicile cannot be measured directly, it is assumed that the choice of structure is indicative of the value that the household places on one choice over another.

% \begin{itemize}
% 
%   \item Differences in energy use by race and ethnicity is frequently reported in the literature
%   \item Much of the difference has to do with differences in income levels and education but not frequently modeled correctly.
%   \item Even with proper race and ethnicity controls with income, some patterns persist.
%   \item We assert that these differences are caused, at least in part, by housing discrimination, forcing people into housing types different than what they would prefer without discrimination; and renting rather than buying.
%   \item We show this with a model that endogenizes structure type and tenure decision.
%   \item emphasize that this is early work.
% \end{itemize}

@@

RECS data set is the 2009 publication.  12083 observations are included in the data, of which 11395 are included in the struture-tenure model. Combining dwelling type (dwltype) and the binary response variable Ownrent,Dwltype includes six categories as follows: single family detached house, townhouse (including duplex, or row house), small apartment complex, large apartment complex, mobile home. Mobile homes are notable for having considerably fewer observations than other categories. The model is based on the following variables: income, resident ages, education, and ethnicity.  Logged, midpoints, are used for income. Education is broken into six categories describing highest education level completed by the head of the household: elementary, some high school, high school. Some college/trade/vocational school, college graduate and post graduate degree.  The ethnicity variable is constructed from a composite of six dummy variables for head of households broken into head of households one and two.  The result is one variable for each where from one to six: Native American, Asian/Pacific Islander, Black/African American, Hispanic/Latino, White/Caucasian, and Other.  For our purposes head of household #2 is ignored.

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Tue Mar 31 23:55:45 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Mobile & SFDetached & SFAttached & SmApartment & LgApartment \\ 
  \hline
FALSEWt & 371 & 5694 & 544 & 430 & 951 \\ 
  FALSEAfAm &  24 & 754 & 121 & 174 & 382 \\ 
  FALSEAsian &   1 & 231 &  48 &  52 & 113 \\ 
  FALSEMulti &   6 &  87 &  14 &  12 &  27 \\ 
  FALSENativeAm &   7 &  35 &   9 &   7 &  15 \\ 
  FALSEOther &   2 &  59 &   8 &  13 &  29 \\ 
  FALSEPacific &   1 &  22 &   1 &   2 &  10 \\ 
  TRUEAfAm &   3 &   8 &  10 &   5 &   8 \\ 
  TRUEAsian &   0 &   5 &   0 &   0 &   1 \\ 
  TRUEMulti &   1 &  10 &   2 &   4 &   4 \\ 
  TRUENativeAm &   2 &  17 &   3 &   6 &   9 \\ 
  TRUEOther &   6 &  41 &  12 &  16 &  24 \\ 
  TRUEPacific &   0 &   2 &   1 &   1 &   0 \\ 
  TRUEWt &  97 & 730 & 105 & 184 & 332 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Race and Structure Type} 
\label{tab:RaceVStruct}
\end{table}
% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Tue Mar 31 23:55:45 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & Mobile & SFDetached & SFAttached & SmApartment & LgApartment \\ 
  \hline
NE &  47 & 1173 & 218 & 326 & 470 \\ 
  MidWest &  92 & 2080 & 162 & 145 & 323 \\ 
  South & 245 & 2685 & 257 & 226 & 603 \\ 
  West & 137 & 1757 & 241 & 209 & 509 \\ 
   \hline
\end{tabular}
\caption{Count of Observations by Region and Structure Type} 
\label{tab:RegionVStruct}
\end{table}
\begin{figure}
\begin{center}
\caption{Annual kWh by Rent/Own and Race}
\label{fig:kWhbyOwnRace}
\includegraphics{DraftEdwardsWoods-005}
\end{center}
\end{figure}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Tue Mar 31 23:56:20 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & FALSE & TRUE \\ 
  \hline
FALSEWt & 7606 & 384 \\ 
  FALSEAfAm & 1367 &  88 \\ 
  FALSEAsian & 424 &  21 \\ 
  FALSEMulti & 133 &  13 \\ 
  FALSENativeAm &  68 &   5 \\ 
  FALSEOther & 102 &   9 \\ 
  FALSEPacific &  30 &   6 \\ 
  TRUEAfAm &  31 &   3 \\ 
  TRUEAsian &   4 &   2 \\ 
  TRUEMulti &  19 &   2 \\ 
  TRUENativeAm &  36 &   1 \\ 
  TRUEOther &  88 &  11 \\ 
  TRUEPacific &   4 &   0 \\ 
  TRUEWt & 1330 & 118 \\ 
   \hline
\end{tabular}
\caption{EnergyStar Wall AC by Race and Ethnicity} 
\label{tab:EnergyStarWall}
\end{table}

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Tue Mar 31 23:56:20 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrr}
  \hline
 & Rural & Urban \\ 
  \hline
FALSEWt & 1937 & 6053 \\ 
  FALSEAfAm & 192 & 1263 \\ 
  FALSEAsian &  14 & 431 \\ 
  FALSEMulti &  28 & 118 \\ 
  FALSENativeAm &  25 &  48 \\ 
  FALSEOther &  12 &  99 \\ 
  FALSEPacific &   4 &  32 \\ 
  TRUEAfAm &   6 &  28 \\ 
  TRUEAsian &   0 &   6 \\ 
  TRUEMulti &   1 &  20 \\ 
  TRUENativeAm &   3 &  34 \\ 
  TRUEOther &   5 &  94 \\ 
  TRUEPacific &   2 &   2 \\ 
  TRUEWt & 137 & 1311 \\ 
   \hline
\end{tabular}
\caption{Race by Urban/Rural} 
\label{tab:UrbRural}
\end{table}

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Tue Mar 31 23:56:20 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrr}
  \hline
 & NG & LPG & Oil & Kerosene & Elec & Wood & Solar & Other \\ 
  \hline
FALSEWt & 4077 & 315 & 361 &   3 & 3190 &  11 &  12 &   7 \\ 
  FALSEAfAm & 755 &  17 &  35 &   0 & 640 &   0 &   2 &   0 \\ 
  FALSEAsian & 312 &   7 &  12 &   0 & 109 &   0 &   0 &   2 \\ 
  FALSEMulti &  85 &   5 &   3 &   0 &  53 &   0 &   0 &   0 \\ 
  FALSENativeAm &  34 &   2 &   1 &   0 &  36 &   0 &   0 &   0 \\ 
  FALSEOther &  57 &   3 &   6 &   0 &  44 &   0 &   0 &   0 \\ 
  FALSEPacific &  15 &   0 &   2 &   0 &  17 &   0 &   2 &   0 \\ 
  TRUEAfAm &  20 &   0 &   1 &   0 &  13 &   0 &   0 &   0 \\ 
  TRUEAsian &   5 &   0 &   0 &   0 &   1 &   0 &   0 &   0 \\ 
  TRUEMulti &  12 &   0 &   1 &   0 &   8 &   0 &   0 &   0 \\ 
  TRUENativeAm &  29 &   0 &   0 &   0 &   8 &   0 &   0 &   0 \\ 
  TRUEOther &  62 &   1 &   5 &   0 &  30 &   0 &   0 &   0 \\ 
  TRUEPacific &   1 &   1 &   0 &   0 &   2 &   0 &   0 &   0 \\ 
  TRUEWt & 830 &  33 &  26 &   0 & 552 &   0 &   1 &   0 \\ 
   \hline
\end{tabular}
\caption{Water Service by Race and Ethnicity} 
\label{tab:Water}
\end{table}
% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Tue Mar 31 23:56:20 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrrrr}
  \hline
 & NG & LPG & Oil & Kerosene & Elec & Wood & Solar & District & Other \\ 
  \hline
FALSEWt & 3987 & 400 & 642 &  40 & 2515 & 245 &   1 &  11 &  19 \\ 
  FALSEAfAm & 674 &  29 &  60 &   6 & 640 &  10 &   0 &   5 &   0 \\ 
  FALSEAsian & 249 &   1 &  21 &   0 & 122 &   1 &   0 &   2 &   0 \\ 
  FALSEMulti &  80 &   6 &   7 &   0 &  41 &   7 &   0 &   0 &   1 \\ 
  FALSENativeAm &  34 &   3 &   1 &   0 &  33 &   2 &   0 &   0 &   0 \\ 
  FALSEOther &  59 &   1 &   9 &   0 &  36 &   3 &   0 &   0 &   0 \\ 
  FALSEPacific &  16 &   0 &   2 &   0 &   5 &   1 &   0 &   0 &   0 \\ 
  TRUEAfAm &  21 &   0 &   1 &   1 &   9 &   0 &   0 &   0 &   0 \\ 
  TRUEAsian &   4 &   0 &   0 &   0 &   1 &   0 &   0 &   0 &   0 \\ 
  TRUEMulti &  11 &   0 &   4 &   0 &   4 &   1 &   0 &   0 &   0 \\ 
  TRUENativeAm &  26 &   1 &   2 &   0 &   7 &   0 &   0 &   0 &   0 \\ 
  TRUEOther &  53 &   0 &   8 &   1 &  32 &   0 &   0 &   2 &   0 \\ 
  TRUEPacific &   1 &   0 &   0 &   0 &   2 &   0 &   0 &   0 &   0 \\ 
  TRUEWt & 604 &  25 &  51 &   2 & 540 &  18 &   0 &   3 &   1 \\ 
   \hline
\end{tabular}
\caption{Heating Fuel by Race and Ethnicity} 
\label{tab:HeatFuel}
\end{table}
% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Tue Mar 31 23:56:20 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrr}
  \hline
 & VColdCold & HotDryMixedDry & HotHumid & MixedHumid & Marine \\ 
  \hline
FALSEWt & 3118 & 850 & 1216 & 2382 & 424 \\ 
  FALSEAfAm & 299 & 131 & 383 & 611 &  31 \\ 
  FALSEAsian &  95 & 128 &  60 &  77 &  85 \\ 
  FALSEMulti &  51 &  27 &  13 &  40 &  15 \\ 
  FALSENativeAm &  23 &  10 &   7 &  28 &   5 \\ 
  FALSEOther &  29 &  16 &  24 &  37 &   5 \\ 
  FALSEPacific &   4 &   6 &  13 &   4 &   9 \\ 
  TRUEAfAm &  16 &   5 &   4 &   9 &   0 \\ 
  TRUEAsian &   2 &   2 &   1 &   0 &   1 \\ 
  TRUEMulti &  12 &   6 &   1 &   0 &   2 \\ 
  TRUENativeAm &   9 &  14 &   1 &   8 &   5 \\ 
  TRUEOther &  35 &  19 &  10 &  28 &   7 \\ 
  TRUEPacific &   2 &   0 &   2 &   0 &   0 \\ 
  TRUEWt & 237 & 481 & 406 & 237 &  87 \\ 
   \hline
\end{tabular}
\caption{Climate by Race and Ethnicity} 
\label{tab:Climate}
\end{table}
\begin{figure}
\begin{center}
\caption{Age of Structure by Rent/Own and Race/Ethnicity}
\label{fig:AgebyOwnRace}
\includegraphics{DraftEdwardsWoods-013}
\end{center}
\end{figure}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Tue Mar 31 23:56:29 2015
\begin{table}[ht]
\centering
\begin{tabular}{rrrrrrrr}
  \hline
 & Never & ThreeDay & TwoDay & OneDay & FewWeek & OneWeek & LessWeek \\ 
  \hline
FALSEWt &  67 & 452 & 1814 & 3303 & 1825 & 254 & 275 \\ 
  FALSEAfAm &  11 & 156 & 351 & 341 & 448 &  80 &  68 \\ 
  FALSEAsian &   4 &  63 & 111 & 148 &  91 &  13 &  15 \\ 
  FALSEMulti &   2 &  14 &  45 &  40 &  36 &   7 &   2 \\ 
  FALSENativeAm &   0 &   7 &  22 &  27 &  11 &   3 &   3 \\ 
  FALSEOther &   2 &  10 &  25 &  21 &  43 &   3 &   7 \\ 
  FALSEPacific &   0 &   3 &   9 &  10 &  11 &   0 &   3 \\ 
  TRUEAfAm &   1 &   4 &   7 &  13 &   9 &   0 &   0 \\ 
  TRUEAsian &   0 &   0 &   1 &   3 &   2 &   0 &   0 \\ 
  TRUEMulti &   0 &   2 &   1 &  11 &   5 &   2 &   0 \\ 
  TRUENativeAm &   0 &   3 &  12 &  15 &   4 &   2 &   1 \\ 
  TRUEOther &   0 &  20 &  28 &  31 &  14 &   3 &   3 \\ 
  TRUEPacific &   0 &   3 &   0 &   1 &   0 &   0 &   0 \\ 
  TRUEWt &  22 & 208 & 453 & 435 & 226 &  42 &  62 \\ 
   \hline
\end{tabular}
\caption{Weekly Meals Cooked by Race and Ethnicity} 
\label{tab:Cooking}
\end{table}
\begin{figure}
\begin{center}
\caption{Daytime Temp and Race/Ethnicity (Winter)}
\label{fig:TempHomeRace}
\includegraphics{DraftEdwardsWoods-015}
\end{center}
\end{figure}

@@

% latex table generated in R 3.0.1 by xtable 1.7-4 package
% Tue Mar 31 23:56:33 2015
\begin{longtable}{rrrrl}
 & Estimate & Std. Error & t value & Sig \\ 
(Intercept) & -637.3566 & 1754.7664 & -0.3632 &   \\ 
  ElecMealsThreeDay & 1265.5101 & 447.0979 & 2.8305 & * \\ 
  ElecMealsTwoDay & 1548.2300 & 199.6619 & 7.7543 & *** \\ 
  ElecMealsOneDay & 1607.3686 & 186.4168 & 8.6224 & *** \\ 
  ElecMealsFewWeek & 1371.7940 & 201.0134 & 6.8244 & *** \\ 
  ElecMealsOneWeek & 1613.9994 & 446.8554 & 3.6119 & ** \\ 
  ElecMealsLessWeek & 1078.7643 & 420.7528 & 2.5639 & . \\ 
  NUMFRIG & 2043.1588 & 162.1146 & 12.6032 & *** \\ 
  AgeFridge2to4Years & -37.2321 & 219.9343 & -0.1693 &   \\ 
  AgeFridge5to9Years & 189.4846 & 206.9121 & 0.9158 &   \\ 
  AgeFridge20PlusYears & 289.0881 & 442.9034 & 0.6527 &   \\ 
  AgeFridge10to14Years & 390.5240 & 258.1351 & 1.5129 &   \\ 
  AgeFridge15to19Years & -109.7635 & 303.2599 & -0.3619 &   \\ 
  NUMPC & 431.9238 & 75.4693 & 5.7232 & *** \\ 
  TIMEON1OneTo3Hrs & 9.2777 & 182.6120 & 0.0508 &   \\ 
  TIMEON1ThreeTo6Hrs & 35.3052 & 208.4801 & 0.1693 &   \\ 
  TIMEON1SixTo10Hrs & 258.4370 & 294.7298 & 0.8769 &   \\ 
  TIMEON1Gr10 & 929.5422 & 268.3058 & 3.4645 & ** \\ 
  WELLPUMPTRUE & 1182.7020 & 300.5331 & 3.9353 & ** \\ 
  ElecWaterSmall & 4283.1501 & 307.1885 & 13.9431 & *** \\ 
  ElecWaterMed & 4381.2889 & 201.2909 & 21.7660 & *** \\ 
  ElecWaterLrg & 5695.3238 & 300.4903 & 18.9534 & *** \\ 
  ElecWaterTankless & 3171.8175 & 981.4629 & 3.2317 & * \\ 
  SWIMPOOLTRUE & 3603.9817 & 373.1464 & 9.6584 & *** \\ 
  ElecPoolTRUE & 5374.6889 & 1639.6680 & 3.2779 & * \\ 
  RECBATHTRUE & 1865.3790 & 679.7961 & 2.7440 & * \\ 
  ElecTubTRUE & 285.6194 & 837.6762 & 0.3410 &   \\ 
